Growth Resilience (reanalisis)

### 2017-12-15 analysis/bai/analysis_resilience_bai.Rmd
update anovas resiliences

---
title: "Growth Resilience"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 June"
output:
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,warning=FALSE, error=TRUE, message=FALSE)
```

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
library("stringr")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('pander')
library('broom')
library('effects')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
library('car')
library('auxiliar')
library('WRS2')
library('MASS')
library('rcompanion')
```
# Resilience

@@

```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

```{r}
# Replace SNA by SJ and SNB by CA
names(ca) <- stringr::str_replace(names(ca), "SNB", "CA") 
names(sj) <- stringr::str_replace(names(sj), "SNA", "SJ")

@@

```{r}
# Create subset to compare between sites 
caL <- ca[,c("CA0101","CA0102","CA0201","CA0202","CA0301","CA0302","CA0401","CA0402","CA0501","CA0502",
             "CA0601","CA0602","CA0701","CA0702","CA0801","CA0802","CA0901","CA0902","CA1001","CA1002",
             "CA2601","CA2602","CA2701","CA2702","CA2801","CA2802","CA2901","CA2902","CA3001","CA3002")] 
caH <- ca[, c("CA1101","CA1102","CA1201","CA1202","CA1301","CA1302","CA1401","CA1402","CA1501","CA1502",
              "CA1601","CA1602","CA1701","CA1702","CA1801","CA1802","CA1901","CA1902","CA2001","CA2002",
              "CA2101","CA2102","CA2201","CA2202","CA2301","CA2302","CA2401","CA2402","CA2501","CA2502")]

@@

* Computar métricas de resiliencia BAI para los tres sitios. 
* Computar tres eventos climáticos: 1995, 2005, 2012
* Computar dos ventanas temporales: 2 y 3

@@

### Computar correlaciones ventanas temporales 
```{r}
# Vector with objects name
obj <- c('res_2_sj', 'res_3_sj', 'res_4_sj',
         'res_2_caL', 'res_3_caL', 'res_4_caL',
         'res_2_caH', 'res_3_caH', 'res_4_caH')

@@

correlations <- inner_join(cor2, cor3, by='ind') %>% inner_join(cor4, by='ind')

# Resistance
aux_coefs <- c()

@@

grid.arrange(p_rt23, p_rt24, p_rt34,ncol=3)

# Recovery 
model <- lm(rc2~rc3, data=correlations)
p_rc23 <- correlations %>% ggplot(aes(rc2, rc3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rc (R2) = ', round(summary(model)$r.squared, 3))) + 
  theme(legend.position = c(.2, .75))
aux <- as.data.frame(cbind('rc','2-3', as.numeric(summary(model)$r.squared)))
aux_coefs <- rbind(aux_coefs, aux)

@@

grid.arrange(p_rc23, p_rc24, p_rc34,ncol=3)

# Resilience
model <- lm(rs2~rs3, data=correlations)
p_rs23 <- correlations %>% ggplot(aes(rs2, rs3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rs (R2) = ', round(summary(model)$r.squared, 3))) + 
  theme(legend.position = c(.2, .75))
aux <- as.data.frame(cbind('rs','2-3', as.numeric(summary(model)$r.squared)))
aux_coefs <- rbind(aux_coefs, aux)

@@

grid.arrange(p_rs23, p_rs24, p_rs34,ncol=3)

# Relative Resilience
model <- lm(rrs2~rrs3, data=correlations)
p_rrs23 <- correlations %>% ggplot(aes(rrs2, rrs3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rrs (R2) = ', round(summary(model)$r.squared, 3))) + 
  theme(legend.position = c(.2, .75))
aux <- as.data.frame(cbind('rrs','2-3', as.numeric(summary(model)$r.squared)))
aux_coefs <- rbind(aux_coefs, aux)

@@

grid.arrange(p_rrs23, p_rrs24, p_rrs34,ncol=3)

names(aux_coefs) <- c('var', 'window_size', 'r2')

@@

# Plots Crecimiento
## Boxplot with outliers 
```{r}
gsj <- res_3_sj$growth %>% mutate(site='SJ')
gcaL <- res_3_caL$growth %>% mutate(site='caL')
gcaH <- res_3_caH$growth %>% mutate(site='caH')

@@

## Mean + se 
```{r}
g %>% 
  mutate(disturb = dplyr::recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.2) +
  geom_point(size=2, shape=21, fill='white') + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())
```

```{r}
pgrowht <- g %>% 
  mutate(disturb = dplyr::recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb, colour=site)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.15) +
  geom_point(size=3, aes(shape=site), fill='white') + 
  geom_line(aes(group=site))+
  facet_wrap(~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())

@@

@@

```{r}
shapirosNormal <- function(df, resp_var, factor_vars) {
  rv <- enquo(resp_var)
  out <- df %>%
    group_by_(.dots=factor_vars) %>%
    summarise(statistic = round(shapiro.test(!!rv)$statistic,5),
              p_value = round(shapiro.test(!!rv)$p.value,5)) %>%
    data.frame()

@@

```{r}
# See auxiliar::shapirosNormal
### Resilience

@@

```{r}
normtestAB <- rbind(nrcAB, nrtAB, nrsAB, nrrsAB) 
normtestAB %>% pander()
write.csv(normtestAB, 
          file=paste0(di, '/out/anovas_resilience/normo_disturb_year_site.csv'), row.names = F)
```

```{r}
rm(nrcA, nrcB, nrcAB,
   nrsA, nrsB, nrsAB,
   nrrsA, nrrsB, nrrsAB,
   nrtA, nrtB, nrtAB)
```

@@

```{r}
## See auxiliar::homogetest
factores <- c('disturb_year', 'site', 'interaction(disturb_year, site)') 
responses <- c('rs', 'rc', 'rt', 'rrs')
homo <- c()

@@

homo %>% pander()
write.csv(homo, 
          file=paste0(di, '/out/anovas_resilience/homocedasticidad.csv'), row.names = F)
```

@@

@@

```{r}
factores <- c('disturb_year', 'site', 'interaction(disturb_year, site)') 
responses <- c('logrs', 'logrc', 'logrt', 'logrrs')
homo_log <- c()

@@

homo_log %>% pander()
write.csv(homo_log, 
          file=paste0(di, '/out/anovas_resilience/homocedasticidad_log.csv'), row.names = F)
```

@@

## Custom functions

```{r}
# Custom Function to compute ANOVAS
aovas <- function(df, vars, resp_var){ 
  require('dplyr')
  require('broom')

@@

## Recovery 
```{r}
# Variable
resp_var <- 'rc'

@@

```{r, fig.width = 4, fig.height=4}
ps
```

```{r, fig.width = 4, fig.height=4}
pd
```

```{r, fig.width = 4, fig.height=4}
picollapse
```

```{r, fig.width = 6}
pi
```

@@

```{r, fig.width = 4, fig.height=4}
ps
```

```{r, fig.width = 4, fig.height=4}
pd
```

```{r, fig.width = 4, fig.height=4}
picollapse
```

```{r, fig.width = 6}
pi
```

@@

```{r, fig.width = 4, fig.height=4}
ps
```

```{r, fig.width = 4, fig.height=4}
pd
```

```{r, fig.width = 4, fig.height=4}
picollapse
```

```{r, fig.width = 6}
pi
```

@@

```{r, fig.width = 4, fig.height=4}
ps
```

```{r, fig.width = 4, fig.height=4}
pd
```

```{r, fig.width = 4, fig.height=4}
picollapse
```

```{r, fig.width = 6}
pi
```

@@

```{r}
pdf(paste0(di, 'out/fig/resilience/interaction_plotsSE.pdf'), width=9, height = 9)
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
dev.off()

pdf(paste0(di, 'out/fig/resilience/interaction_plotsCI.pdf'), width=9, height = 9)
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
dev.off()

```{r}
aovas_coeff <- aov_rc$model_coeff %>% mutate(var = 'rc') %>% 
  bind_rows(aov_rt$model_coeff %>% mutate(var = 'rt')) %>% 
  bind_rows(aov_rs$model_coeff %>% mutate(var = 'rs')) %>% 
  bind_rows(aov_rrs$model_coeff%>% mutate(var = 'rrs'))

write.csv(aovas_coeff, file=paste0(di, '/out/anovas_resilience/anovas_statistics.csv'), row.names = F)

@@

write.csv(aovas_model_summary, 
          file=paste0(di, '/out/anovas_resilience/anovas_summary_modelos.csv'), row.names = F)

@@

  pbad2way(rs ~ disturb_year + site + disturb_year:site, data = df, 
           est = "mom", nboot = nboot)

@@

@@

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest 
  out$pha <- pha
  out$phb <- phb
  out$phab <- phab

  print(out_ra)
  print(phRWS2)

@@

```{r}
mhuber<- mhuber %>% 
  mutate(var_sorted = case_when(var == "rc" ~ "1_rc",
                                var == "rt" ~ "0_rt",
                                var == "rs" ~ "2_rs",
                                var == "rrs" ~ "3_rrs"))

@@

robust_plot_evi_drought <- ggplot(mhuber, aes(x=disturb_year, y=M.Huber, color = site, group=site, fill=site)) + 
  geom_errorbar(aes(ymin=lower.ci, ymax=upper.ci), 
                width=.1, size=0.7, position=pd) + 
  geom_line(aes(group=site,color=site, linetype=site), position=pd) + 
  geom_point(shape=21, size=3.5, position=pd) +
  facet_wrap(~var_sorted, nrow = 2, scales = 'free_y',
             labeller=as_labeller(c('0_rt' = 'Resistance', 
                                 '1_rc' = 'Recovery',
                                 '2_rs' = 'Resilience',
                                 '3_rrs' = 'Relative Resilience'))) +
  scale_color_manual(values=c('black','blue','red')) + 
  scale_fill_manual(values=c('black','blue','red')) + theme_bw() +
  scale_linetype_manual(values=c("solid", "dashed", 'dashed')) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        legend.position="bottom") +
  ylab('') + xlab('Drought event')

robust_plot_evi_drought

pdf(paste0(di, 'out/fig/resilience/robust_plot_evi_drought.pdf'), width=9, height = 9)
robust_plot_evi_drought 
dev.off()
```

### Response ~ (x=site)
```{r}
pd <- position_dodge(.2)

robust_plot_evi_site <- ggplot(mhuber, aes(x=site, y=M.Huber, color = disturb_year, group=disturb_year, fill=disturb_year)) + 
  geom_errorbar(aes(ymin=lower.ci, ymax=upper.ci), 
                width=.1, size=0.7, position=pd) + 
  geom_line(aes(group=disturb_year,color=disturb_year, linetype=disturb_year), position=pd) + 
  geom_point(shape=21, size=3.5, position=pd) +
  facet_wrap(~var_sorted, nrow = 2, scales = 'free_y',
             labeller=as_labeller(c('0_rt' = 'Resistance', 
                                 '1_rc' = 'Recovery',
                                 '2_rs' = 'Resilience',
                                 '3_rrs' = 'Relative Resilience'))) +
  scale_color_manual(values=c('black','blue')) + 
  scale_fill_manual(values=c('black','blue')) + theme_bw() +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        legend.position="bottom") +
  ylab('') + xlab('Drought event')

robust_plot_evi_site

pdf(paste0(di, 'out/fig/resilience/robust_plot_evi_site.pdf'), width=9, height = 9)
robust_plot_evi_site 
dev.off()
```

```{r}
# Export data 
write.csv(mhuber, file=paste0(di, '/out/anovas_resilience/robust_mhuber.csv'), row.names = F)
write.csv(mhuber_agg, file=paste0(di, '/out/anovas_resilience/robust_mhuber_agg.csv'), row.names = F)
write.csv(mhuber_a, file=paste0(di, '/out/anovas_resilience/robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_agg_a, file=paste0(di, '/out/anovas_resilience/robust_mhuber_agg_a.csv'), row.names = F)
write.csv(mhuber_b, file=paste0(di, '/out/anovas_resilience/robust_mhuber_b.csv'), row.names = F)
write.csv(mhuber_agg_b, file=paste0(di, '/out/anovas_resilience/robust_mhuber_agg_b.csv'), row.names = F)

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/robust_pairwise.csv'), row.names = F)
```

>>>>

---
title: "Growth Resilience (reanalisis)"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output: pdf_document 
bibliography: ../references.bib 
csl: ../ecology.csl
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, warning=FALSE, error=TRUE, message=FALSE)
```

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("dplR")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('stringr')
library('pander')
library('broom')
library('effects')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
library('car')
library('auxiliar')
library('WRS2')
library('MASS')
library('rcompanion')
```
# Resilience

@@

```{r}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep = '')

@@

```{r, echo=FALSE}
# Replace SNA by SJ and SNB by CA
names(ca) <- stringr::str_replace(names(ca), "SNB", "CA") 
names(sj) <- stringr::str_replace(names(sj), "SNA", "SJ")

@@

```{r, echo=FALSE}
# Create subset to compare between sites 
caL <- ca[,c("CA0101","CA0102","CA0201","CA0202","CA0301","CA0302","CA0401","CA0402","CA0501","CA0502",
             "CA0601","CA0602","CA0701","CA0702","CA0801","CA0802","CA0901","CA0902","CA1001","CA1002",
             "CA2601","CA2602","CA2701","CA2702","CA2801","CA2802","CA2901","CA2902","CA3001","CA3002")] 
caH <- ca[, c("CA1101","CA1102","CA1201","CA1202","CA1301","CA1302","CA1401","CA1402","CA1501","CA1502",
              "CA1601","CA1602","CA1701","CA1702","CA1801","CA1802","CA1901","CA1902","CA2001","CA2002",
              "CA2101","CA2102","CA2201","CA2202","CA2301","CA2302","CA2401","CA2402","CA2501","CA2502")]

@@

* Computar métricas de resiliencia BAI para los tres sitios. 
* Computar tres eventos climáticos: 1995, 2005, 2012
* Computar ventanas temporales: 2, 3 y 4

@@

### Computar correlaciones ventanas temporales 
```{r, echo = FALSE}
# Vector with objects name
obj <- c('res_2_sj', 'res_3_sj', 'res_4_sj',
         'res_2_caL', 'res_3_caL', 'res_4_caL',
         'res_2_caH', 'res_3_caH', 'res_4_caH')

@@

correlations <- inner_join(cor2, cor3, by='ind') %>% inner_join(cor4, by='ind')
```

#### Resistance

```{r correla_temporal_window_rt, echo = FALSE}
# Resistance
aux_coefs <- c()

@@

grid.arrange(p_rt23, p_rt24, p_rt34,ncol=3) 
```

#### Recovery

```{r correla_temporal_window_rc, echo = FALSE}
# Recovery 
model <- lm(rc2~rc3, data=correlations)
p_rc23 <- correlations %>% ggplot(aes(rc2, rc3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rc (R2) = ', round(summary(model)$r.squared, 3))) + 
  theme(legend.position = c(.2, .75))
aux <- as.data.frame(cbind('rc','2-3', as.numeric(summary(model)$r.squared)))
aux_coefs <- rbind(aux_coefs, aux)

@@

grid.arrange(p_rc23, p_rc24, p_rc34,ncol=3) 
```

#### Resilience

```{r correla_temporal_window_rs, echo = FALSE}
# Resilience
model <- lm(rs2~rs3, data=correlations)
p_rs23 <- correlations %>% ggplot(aes(rs2, rs3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rs (R2) = ', round(summary(model)$r.squared, 3))) + 
  theme(legend.position = c(.2, .75))
aux <- as.data.frame(cbind('rs','2-3', as.numeric(summary(model)$r.squared)))
aux_coefs <- rbind(aux_coefs, aux)

@@

grid.arrange(p_rs23, p_rs24, p_rs34,ncol=3) 
```

#### Relative Resilience

```{r correla_temporal_window_rrs, echo = FALSE}
# Relative Resilience
model <- lm(rrs2~rrs3, data=correlations)
p_rrs23 <- correlations %>% ggplot(aes(rrs2, rrs3)) + 
  geom_point(aes(colour=site.x)) + theme_bw() + geom_smooth(method = 'lm', se=FALSE) + 
  ggtitle(paste('rrs (R2) = ', round(summary(model)$r.squared, 3))) + 
  theme(legend.position = c(.2, .75))
aux <- as.data.frame(cbind('rrs','2-3', as.numeric(summary(model)$r.squared)))
aux_coefs <- rbind(aux_coefs, aux)

@@

grid.arrange(p_rrs23, p_rrs24, p_rrs34,ncol=3) 
```

#### Coeficientes de correlacion entre ventanas temporales

```{r echo=FALSE}
# Export correlations window size 
names(aux_coefs) <- c('var', 'window_size', 'r2')

@@

# Plots Crecimiento
## Boxplot with outliers 
```{r growth_disturbances_boxplot, echo = FALSE}
gsj <- res_3_sj$growth %>% mutate(site='SJ')
gcaL <- res_3_caL$growth %>% mutate(site='caL')
gcaH <- res_3_caH$growth %>% mutate(site='caH')

@@

## Mean + se 
```{r growth_disturbances_mean_se, echo = FALSE}
g %>% 
  mutate(disturb = dplyr::recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.2) +
  geom_point(size=2, shape=21, fill='white') + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())
```

```{r growth_disturbances_mean_se_colours, echo = FALSE}
pgrowht <- g %>% 
  mutate(disturb = dplyr::recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb, colour=site)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.15) +
  geom_point(size=3, aes(shape=site), fill='white') + 
  geom_line(aes(group=site))+
  facet_wrap(~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  scale_shape_manual(values=c(15,19,19)) + 
  theme(panel.grid = element_blank())

@@

## tables

@@

```{r, echo = FALSE}
shapirosNormal <- function(df, resp_var, factor_vars) {
  rv <- enquo(resp_var)
  out <- df %>%
    group_by_(.dots=factor_vars) %>%
    summarise(statistic = round(shapiro.test(!!rv)$statistic,5),
              p_value = round(shapiro.test(!!rv)$p.value,5)) %>%
    data.frame()

@@

```{r, echo = FALSE}
# See auxiliar::shapirosNormal
### Resilience

@@

```{r}
normtestA <- rbind(nrcA, nrtA, nrsA, nrrsA) 
normtestA %>% pander()
write.csv(normtestA, 
          file=paste0(di, '/out/anovas_resilience/bai/normo_disturb_year.csv'), row.names = F)
```

```{r}
normtestB <- rbind(nrcB, nrtB, nrsB, nrrsB) 
normtestB %>% pander()
write.csv(normtestB, 
          file=paste0(di, '/out/anovas_resilience/bai/normo_site.csv'), row.names = F)
```

```{r}
normtestAB <- rbind(nrcAB, nrtAB, nrsAB, nrrsAB) 
normtestAB %>% pander()
write.csv(normtestAB, 
          file=paste0(di, '/out/anovas_resilience/bai/normo_disturb_year_site.csv'), row.names = F)
```

```{r}
# rm(nrcA, nrcB, nrcAB,
#    nrsA, nrsB, nrsAB,
#    nrrsA, nrrsB, nrrsAB,
#    nrtA, nrtB, nrtAB)
```

@@

```{r, echo = FALSE}
## See auxiliar::homogetest
factores <- c('disturb_year', 'site', 'interaction(disturb_year, site)') 
responses <- c('rs', 'rc', 'rt', 'rrs')
homo <- c()

@@

homo %>% pander()
write.csv(homo, 
          file=paste0(di, '/out/anovas_resilience/bai/homocedasticidad.csv'), row.names = F)
```

@@

# Transformación datos

## Log

@@

```{r, echo = FALSE}
factores <- c('disturb_year', 'site', 'interaction(disturb_year, site)') 
responses <- c('logrs', 'logrc', 'logrt', 'logrrs')
homo_log <- c()

@@

homo_log %>% pander()
write.csv(homo_log, 
          file=paste0(di, '/out/anovas_resilience/bai/homocedasticidad_log.csv'), row.names = F)
```

@@

# ANOVAS

* Utilizamos una custom function

```{r, echo = FALSE}
# Custom Function to compute ANOVAS
aovas <- function(df, vars, resp_var){ 
  require('dplyr')
  require('broom')

@@

## Recovery 
```{r, echo=FALSE}
# Variable
resp_var <- 'rc'

@@

```{r aov_rc_site, fig.width = 4, fig.height=4}
ps
```

```{r aov_rc_disturb, fig.width = 4, fig.height=4}
pd
```

```{r aov_rc_inter_collapse, fig.width = 4, fig.height=4}
picollapse
```

```{r aov_rc_inter, fig.width = 6}
pi
```

@@

```{r aov_rt_site, fig.width = 4, fig.height=4}
ps
```

```{r aov_rt_disturb, fig.width = 4, fig.height=4}
pd
```

```{r aov_rt_inter_collapse, fig.width = 4, fig.height=4}
picollapse
```

```{r aov_rt_inter, fig.width = 6}
pi
```

@@

```{r aov_rrs_site, fig.width = 4, fig.height=4}
ps
```

```{r aov_rrs_disturb, fig.width = 4, fig.height=4}
pd
```

```{r aov_rrs_inter_collapse, fig.width = 4, fig.height=4}
picollapse
```

```{r aov_rrs_inter, fig.width = 6}
pi
```

@@

```{r aov_rs_site, fig.width = 4, fig.height=4}
ps
```

```{r aov_rs_disturb, fig.width = 4, fig.height=4}
pd
```

```{r aov_rs_inter_collapse, fig.width = 4, fig.height=4}
picollapse
```

```{r aov_rs_inter, fig.width = 6}
pi
```

@@

### mean + sd
```{r plot_resiliences_bai_sd,fig.width = 12, fig.height=12}
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
```

### mean + ci
```{r plot_resiliences_bai_ci, fig.width = 12, fig.height=12}
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
```

```{r, echo=FALSE}
pdf(paste0(di, '/out/mean_resilience/bai/interaction_plotsSE.pdf'), width=9, height = 9)
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
dev.off()

pdf(paste0(di, '/out/mean_resilience/bai/interaction_plotsCI.pdf'), width=9, height = 9)
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
dev.off()
```

```{r, echo=FALSE}
aovas_coeff <- aov_rc$model_coeff %>% mutate(var = 'rc') %>% 
  bind_rows(aov_rt$model_coeff %>% mutate(var = 'rt')) %>% 
  bind_rows(aov_rs$model_coeff %>% mutate(var = 'rs')) %>% 
  bind_rows(aov_rrs$model_coeff%>% mutate(var = 'rrs'))

write.csv(aovas_coeff, file=paste0(di, '/out/anovas_resilience/bai/anovas_statistics.csv'), row.names = F)

@@

write.csv(aovas_model_summary, 
          file=paste0(di, '/out/anovas_resilience/bai/anovas_summary_modelos.csv'), row.names = F)

@@

@@

  out_raTrimmed <- t2way(formulaFull, data = df)

  out_ratr_df <- data.frame(fact = c(out_raTrimmed$varnames[2], 
                                    out_raTrimmed$varnames[3], 
                                    paste0(out_raTrimmed$varnames[2], ':', out_raTrimmed$varnames[3])),
              statistic = c(out_raTrimmed$Qa, out_raTrimmed$Qb, out_raTrimmed$Qab),
              pvalue = c(out_raTrimmed$A.p.value, out_raTrimmed$B.p.value, out_raTrimmed$AB.p.value))

@@

  phtrimmed <- mcp2atm(formulaFull, data=df)

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$raTrimmed <- out_raTrimmed
  out$out_ratr_df <- out_ratr_df
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest 
  out$pha <- pha
  out$phb <- phb
  out$phab <- phab

  print(cat('\n Robust M-Anova \n'))
  print(out_ra)
  print(cat('\n Robust Trimmed \n'))
  print(out_raTrimmed)
  print(cat('\n post hoc Mhuber \n'))
  print(phRWS2)
  print(cat('\n post hoc Trimmed means \n'))
  print(phtrimmed)

@@

```{r robust_plot_bai_drought}
mhuber<- mhuber %>% 
  mutate(var_sorted = case_when(var == "rc" ~ "1_rc",
                                var == "rt" ~ "0_rt",
                                var == "rs" ~ "2_rs",
                                var == "rrs" ~ "3_rrs"))

@@

robust_plot_bai_drought <- ggplot(mhuber, aes(x=disturb_year, y=M.Huber, color = site, group=site, fill=site)) + 
  geom_errorbar(aes(ymin=lower.ci, ymax=upper.ci), 
                width=.1, size=0.7, position=pd) + 
  geom_line(aes(group=site,color=site, linetype=site), position=pd) + 
  geom_point(shape=21, size=3.5, position=pd) +
  facet_wrap(~var_sorted, nrow = 2, scales = 'free_y',
             labeller=as_labeller(c('0_rt' = 'Resistance', 
                                 '1_rc' = 'Recovery',
                                 '2_rs' = 'Resilience',
                                 '3_rrs' = 'Relative Resilience'))) +
  scale_color_manual(values=c('black','blue','red')) + 
  scale_fill_manual(values=c('black','blue','red')) + theme_bw() +
  scale_linetype_manual(values=c("solid", "dashed", 'dashed')) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        legend.position="bottom") +
  ylab('') + xlab('Drought event')

robust_plot_bai_drought

pdf(paste0(di, 'out/resilience_robust/bai/robust_plot_bai_drought.pdf'), width=9, height = 9)
robust_plot_bai_drought 
dev.off()
```

### Response ~ (x=site)
```{r robust_plot_bai_site}
pd <- position_dodge(.2)

robust_plot_bai_site <- ggplot(mhuber, aes(x=site, y=M.Huber, color = disturb_year, group=disturb_year, fill=disturb_year)) + 
  geom_errorbar(aes(ymin=lower.ci, ymax=upper.ci), 
                width=.1, size=0.7, position=pd) + 
  geom_line(aes(group=disturb_year,color=disturb_year, linetype=disturb_year), position=pd) + 
  geom_point(shape=21, size=3.5, position=pd) +
  facet_wrap(~var_sorted, nrow = 2, scales = 'free_y',
             labeller=as_labeller(c('0_rt' = 'Resistance', 
                                 '1_rc' = 'Recovery',
                                 '2_rs' = 'Resilience',
                                 '3_rrs' = 'Relative Resilience'))) +
  scale_color_manual(values=c('black','blue')) + 
  scale_fill_manual(values=c('black','blue')) + theme_bw() +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        legend.position="bottom") +
  ylab('') + xlab('Drought event')

robust_plot_bai_site

pdf(paste0(di, 'out/resilience_robust/bai/robust_plot_bai_site.pdf'), width=9, height = 9)
robust_plot_bai_site 
dev.off()
```

```{r}

rars$out_ratr_df$var <- 'rs'
rarc$out_ratr_df$var <- 'rc'
rart$out_ratr_df$var <- 'rt'
rarrs$out_ratr_df$var <- 'rrs'

trimmedanovas <- rbind(rarc$out_ratr_df, rart$out_ratr_df, rars$out_ratr_df, rarrs$out_ratr_df) 
trimmedanovas %>% pander()

```{r}
# Export data 
write.csv(mhuber, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber.csv'), row.names = F)
write.csv(mhuber_agg, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_agg.csv'), row.names = F)
write.csv(mhuber_a, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_agg_a, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_agg_a.csv'), row.names = F)
write.csv(mhuber_b, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_b.csv'), row.names = F)
write.csv(mhuber_agg_b, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_mhuber_agg_b.csv'), row.names = F)

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/huber_bai/robust_pairwise.csv'), row.names = F)

write.csv(trimmedanovas, file=paste0(di, '/out/anovas_resilience/huber_bai/trimmed_anovas.csv'), row.names = F)
```
